Exploring and Validating the Motives Behind API Evolution: A Case Study

### 2015-03-20 rmtw/a6/latex8.tex
Changed some wurdz
dsaasd

To reduce risks of research bias and human error, the data collection was performed by both researchers individually and independently. If the data differed, the cause was investigated and resolved.

@@

Following the analysis of the archival data, the results of the interviews were analysed. The interviews were analysed using the same approach taken for the archival data. The results of this analysis was then compared and correlated with the results of the code analysis.

We took the same approach (roles/double stuff) as in the collection to reduce human rerror + reseach bias.

>>>>

To reduce risks of research bias and human errors, the data collection was performed independently by both researchers. If the data differed, the cause was investigated and resolved.

@@

Following the analysis of the archival data, the results of the interviews were analysed. The interviews were analysed using the same approach taken for the archival data. The results of this analysis was then compared and correlated with the results of the code analysis, with the goal of confirming the hypotheses that were formulated.

The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.
